Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
Update count interpretation

\begin{table}
\todo{extend this table to have counts with new results}
\centering
\input{tables/perf_summary_13.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations relative to results when imputing on base table. Queries optimized for quality ($\alpha=0$) generally achieve
    lower error than queries optimized for efficiency ($\alpha=1$). Count values reflect the SMAPE over the number of tuples
    used for each configuration with respect to the number of tuples used when executing the query after base table imputation. A higher
    count difference reflects more potential for errors.}
\label{table:smape}
\end{table}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\begin{table}
\centering
\input{tables/perf_summary_13.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations relative to results when imputing on the base table. Queries optimized
    for quality ($\alpha=0$) generally achieve lower error than queries optimized for
    efficiency ($\alpha=1$). Count shares show the number of results returned from each
    query as a percentage of the number of results returned when imputing on the base table.
    A lower count share reflects more potential for errors.}
\label{table:smape}
\end{table}

@@

%%% Local Variables:

%%% mode: latex
%%% TeX-master: "main"
%%% End:
